---
title: "Exploratory Analysis"
output: html_document
---

```{r setup, include=FALSE}
source("exploratory_analysis.R")
library(ggplot2)
knitr::opts_chunk$set(echo = FALSE)
```

## Distribution of Variables
```{r, echo = FALSE, warning=FALSE}
plot_hist
```

In the histogram above, we can see the mean of the variable 'Average Hospital Stay Length' distributed by country. The dataset provides the average hospital stay length per country for all years from 2000 to 2017. We averaged the average hospital stay length across years to get a single value per country, and these values are shown in the distribution. As can be seen in the graph, the average length ranges from  4 to 18 years. The majority of countries have an average hospital stay length of around 8 days. Very few countries have an average hospital stay length of 10 days or greater.

This histogram shows us that many countries have long average hospital stay lengths, but this does not tell us a lot about healthcare utilization. It would be interesting to compare this to the average hospital stay length for all countries, and see which countries are higher and which countries are lower than the world average.
